---
title: "Reproducible reports in R Markdown"
author: "Jacquie Tran | @jacquietran | 18 Aug 2020"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}

options(htmltools.dir.version = FALSE)

# Load libraries
library(xaringanthemer)
library(paletteer)

```

```{r xaringan-themer, include=FALSE, warning=FALSE}

style_duo_accent_inverse(
  primary_color = "#E84A5F",
  secondary_color = "#FF847C"
)
```

class: inverse, center, middle

# From academia to industry

---
class: right, bottom
background-image: url()

Image credit: []()

---
background-image: url()

---

## Starting from the middle of a data project

Where did the data come from?

--

What was done to the data?

--

Why did they make these choices?

--

How did they produce their outputs?

---
class: inverse, center, middle

# Is there a better way?

---
class: inverse, center, middle

# What makes a report reproducible?

---

> "Statisticians write a lot of reports, describing the results of data analyses.
>
> It’s best if such reports are fully reproducible: that **the data and code are available**, and that there’s a **clear and automatic path from data and code to the final report**."
> 
> [Karl Broman](https://kbroman.org/Tools4RR/assets/lectures/03_knitr_Rmd_withnotes.pdf)

---
class: inverse, center, middle

# Why does reproducibility matter?

---

# It matters:

For science

--

For organisations

--

For future you!

---
class: inverse, center, middle

# Case study

## From pilot project to research programme

